Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-02-16 src/tex/ms.tex
Add emcee citation and unit paragraph

In principle, we should only accept solutions that exactly reproduce the LVK
posterior samples in the GW-observable space. However, it is not feasible to
achieve such a condition in practice, therefore we relax the condition in
eq.~\ref{eq:loss} to a small acceptance threshold. For this study, we picked a
threshold of $10^{-2}$. To make sure we find a reasonably complete set of
progenitor parameters that corresponds to the posterior sample point, we use
1000 different initial guesses in solving the optimization problem. As long as
the solution fulfills the acceptance criteria, the root is as valid as all other
roots that fulfill the same acceptance criteria, \emph{regardless to its initial
guess}. This means, we have the freedom to choose the set of initial guesses
however we think might benefit the optimization.

>>>>

In principle, we should only accept solutions that exactly reproduce the LVK
posterior samples in the GW-observable space. However, it is not feasible to
achieve such a condition in practice, therefore we relax the condition in
eq.~\ref{eq:loss} to a small acceptance threshold. For this study, we picked a
threshold of $10^{-2}$ \textbf{solar mass. For a more general study that use
observables that are not with the same unit, the norm should be chosen in a way
that all parameters are represented on a comparable scale.} To make sure we find
a reasonably complete set of progenitor parameters that corresponds to the
posterior sample point, we use 1000 different initial guesses in solving the
optimization problem. As long as the solution fulfills the acceptance criteria,
the root is as valid as all other roots that fulfill the same acceptance
criteria, \emph{regardless to its initial guess}. This means, we have the
freedom to choose the set of initial guesses however we think might benefit the
optimization.
